\newpage
\thispagestyle{empty}

\begin{center}

\huge{Abstract}\\[0.5cm]
\normalsize
\textsc Automatic Face Recognition Technologies have seen dramatic improvements in performance over the past
years and such systems are now widely used for security and commercial applications. An automated system for human
face recognition in a real time background for a company to mark the attendance of the employees.
So smart Attendance using Real Time Face Recognition is a real world solution which comes with day to day activities
of handling employees. The task is very difficult as the real time background subtraction in an image is still a challenge.
To detect real time human face are used to recognize the face detected with a high accuracy rate. The matched face is
used to mark attendance of the employee.
Our system maintains te attendance records of employees automatically. Manual Entering of in logbooks becomes a
difficult task and it also wastes the time. So we designed an efficient module that comprises of face recognition to manage
the attendance records of employees. Our module enrolls the staff ’s face. This enrolling is a onetime process and their
face will be stored in the database. During enrolling of face we require a system since it is a onetime process. You can
have your own roll number as your employee id which will be unique for each employee.
The presence of each employee will be updated in a database. The results showed improved performance over manual
after employee identification. This product gives much more solutions with accurate results in user interactive manner
rather than existing attendance and leave management system.
\\

In colleges, universities, organizations, schools, and offices, taking attendance is one of the most important tasks that must be done on a daily basis. The majority of the time,\\
it is done manually, such as by calling by name or by roll number. The main goal of this project is to create a Face Recognition-based attendance system that will turn this manual process into an automated one. This project meets the requirements for bringing modernization to the way attendance is handled, as well as the criteria for time management. This device is installed in the classroom, where and student's information, such as name, roll number, class, sec, and photographs, is trained. The images are extracted using Open CV. Before the start of the corresponding class, the student can approach the machine, which will begin taking pictures and comparing them to the qualified dataset. Logitech C270 web camera and NVIDIA Jetson Nano Developer kit were used in this project as the camera and processing board. The image is processed as follows: first, faces are identified using a Haarcascade classifier, then faces are recognized using the LBPH (Local Binary Pattern Histogram) Algorithm, histogram data is checked against an established dataset, and the device automatically labels attendance. An Excel sheet is developed, and it is updated every hour with the information from the respective class instructor. 
 
Keywords: Face Detection, Face Recognition, HaarCascade classifier, NVIDIA Jetson Nano 

\\[2.0cm]

\end{center}
\normalsize 



